---
title: "Descriptive Statistics for Crossmodality Toolkit"
author: "Alan Nielsen"
date: "November 1, 2017"
output:
  html_document:
    keep_md: true
---


```{r Libraries and Data, message = FALSE, warning = FALSE}
TrimData <- read.csv("F:/Github Repos/CMT/Data/TrimData.csv")

library(plyr)
library(tidyverse)

TrimData$DataSet <- factor(TrimData$DataSet, c("Pilot", "Main", "Affect", "Color"))

```


```{r Response Means}

Agg1 <- aggregate(Response~Comparison, data=TrimData, mean)
means<- as.data.frame(xtabs(Response ~ Comparison, data=Agg1))

means

rm(means, Agg1)
```

So we can look at that table of means- it's nice but not that exciting- what we instead want to do is look at a heatmap of our results - 

```{r First Heatmap of All Data}

TrimDataAgg <- aggregate(Response ~ Inducer + Concurrent + Comparison,
                     data= TrimData, mean)

Domains <- sort(unique(TrimDataAgg$Inducer))
HighValues <- c("Excited/Bored", "Happy/Sad", "Pleased/Disgusted", "Stressed/Calm",
                "Loud/Quiet", "Bright/Dark", "Red/Blue", "Red/Green", "Red/Yellow",
                "Yellow/Blue", "Noisy/Tonal", "High/Low (Pitch)", "Jagged/Curvy", 
                "Large/Small", "Fast/Slow")

TrimDataAgg$Inducer <- mapvalues(TrimDataAgg$Inducer, from = Domains, to= HighValues)
TrimDataAgg$Concurrent <- mapvalues(TrimDataAgg$Concurrent, from = Domains, to= HighValues)

TrimDataAgg$Inducer <- factor(TrimDataAgg$Inducer,
                           c("Jagged/Curvy", "Large/Small", "Fast/Slow",
                             "Loud/Quiet", "Noisy/Tonal", "High/Low (Pitch)",
                             "Bright/Dark",
                             "Red/Blue", "Red/Green", "Red/Yellow", "Yellow/Blue",
                             "Excited/Bored", "Happy/Sad", "Pleased/Disgusted", "Stressed/Calm" ))

TrimDataAgg$Concurrent <- factor(TrimDataAgg$Concurrent,
                           c("Jagged/Curvy", "Large/Small", "Fast/Slow",
                             "Loud/Quiet", "Noisy/Tonal", "High/Low (Pitch)",
                             "Bright/Dark",
                             "Red/Blue", "Red/Green", "Red/Yellow", "Yellow/Blue",
                             "Excited/Bored", "Happy/Sad", "Pleased/Disgusted", "Stressed/Calm" ))

ggplot(data= TrimDataAgg, aes(x=Concurrent, y=Inducer, fill=Response)) +
  geom_tile(color = "white") +
  ggtitle("Biases - All Data") +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0.5, limit = c(0,1),
                       name="Direction and Strength of Associaton") +
  geom_text(aes(label = round(Response, 2)), size = 4) +
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed() 


ggsave("Heatmap of All Data.png", plot = last_plot(), device = NULL, path = NULL,
  width = 10, height = 8, units = c("in", "cm", "mm"),
  dpi = 600)


```


```{r HeatMap Facet Grid for Each DataSet}

TrimDataAgg2 <- aggregate(Response ~ DataSet + Inducer + Concurrent + Comparison,
                     data= TrimData, mean)

Domains <- sort(unique(TrimDataAgg2$Inducer))
HighValues <- c("Excited/Bored", "Happy/Sad", "Pleased/Disgusted", "Stressed/Calm",
                "Loud/Quiet", "Bright/Dark", "Red/Blue", "Red/Green", "Red/Yellow",
                "Yellow/Blue", "Noisy/Tonal", "High Pitch/Low Pitch", "Jagged/Curvy", 
                "Large/Small", "Fast/Slow")

TrimDataAgg2$Inducer <- mapvalues(TrimDataAgg2$Inducer, from = Domains, to= HighValues)
TrimDataAgg2$Concurrent <- mapvalues(TrimDataAgg2$Concurrent, from = Domains, to= HighValues)

TrimDataAgg2$Inducer <- factor(TrimDataAgg2$Inducer,
                           c("Jagged/Curvy", "Large/Small", "Fast/Slow",
                             "Loud/Quiet", "Noisy/Tonal", "High/Low (Pitch)",
                             "Bright/Dark",
                             "Red/Blue", "Red/Green", "Red/Yellow", "Yellow/Blue",
                             "Excited/Bored", "Happy/Sad", "Pleased/Disgusted", "Stressed/Calm" ))

TrimDataAgg2$Concurrent <- factor(TrimDataAgg2$Concurrent,
                           c("Jagged/Curvy", "Large/Small", "Fast/Slow",
                             "Loud/Quiet", "Noisy/Tonal", "High/Low (Pitch)",
                             "Bright/Dark",
                             "Red/Blue", "Red/Green", "Red/Yellow", "Yellow/Blue",
                             "Excited/Bored", "Happy/Sad", "Pleased/Disgusted", "Stressed/Calm" ))


ggplot(data= TrimDataAgg2, aes(x=Concurrent, y=Inducer, fill=Response)) +
  geom_tile(color = "white") +
  ggtitle("Biases - All DataSets - Faceted") +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0.5, limit = c(0,1),
                       name="Direction and Strength of Associaton") +
  geom_text(aes(label = round(Response, 2)), size = 3) +
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed() +
  facet_wrap(~ DataSet, ncol = 2)


ggsave("Heatmaps by DataSet.png", plot = last_plot(), device = NULL, path = NULL,
  width = 12, height = 10, units = c("in", "cm", "mm"),
  dpi = 600)


```


How well did our Pilot Data Predict our Main Experiment Data?

```{r Subtracting the dataframe}

MainDataAgg <- subset(TrimDataAgg2, DataSet == "Main")
PilotDataAgg <- subset(TrimDataAgg2, DataSet == "Pilot")

DiffDataAgg <- MainDataAgg

DiffDataAgg$DataSet <- "Difference"

DiffDataAgg$Difference <- abs(MainDataAgg$Response - PilotDataAgg$Response)

ggplot(data= DiffDataAgg, aes(x=Concurrent, y=Inducer, fill=Difference)) +
  geom_tile(color = "white") +
  ggtitle("Difference Between Pilot Data and Main Experiment Data") +
  scale_fill_gradient2(low = "white", high = "red", 
                       name="Mismatch") +
  geom_text(aes(label = round(Difference, 2)), size = 3) +
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed()

ggsave("Heatmap of Difference Between Pilot and Main Experiment.png", plot = last_plot(), device = NULL, path = NULL,
  width = 12, height = 10, units = c("in", "cm", "mm"),
  dpi = 600)

```


To that end we are going to do a t-test for every one of our 93 comparisons against chance- because our data aren't normally distributed we want to use a nonparametic statistic- in this case a signed-ranks test.

```{r Wilcoxon, warning = FALSE, message = FALSE}
library(doBy)

TrimDataAgg3 <- summaryBy(Response ~ DataSet + Condition +
                       Inducer + Concurrent + Comparison,
                     data= TrimData, Fun = c(mean))

library(powerAnalysis)
comparisons <- unique(TrimDataAgg$Comparison)
pvals <- list()
zvals <- list()
statvals <- list()
rm(comparison)


for(comparison in comparisons){
  testdata <- subset(TrimDataAgg3, Comparison == comparison)
  
  testres <- wilcox.test(testdata$Response, mu= 0.5, alternative = "two.sided")
  
  pval <- testres$p.value
  pvals <- c(pvals, pval)
  
  testZ <- qnorm(pval/2)
  zvals <- c(zvals, testZ)
  
  teststat <- abs(testZ / (sqrt(nrow(testdata))))
  statvals <- c(statvals, teststat)
  
}

EffSizes <- as.data.frame(cbind(zvals, pvals, statvals))
EffSizes <- cbind(EffSizes, comparisons)

TrimDataAgg$pvalue <- EffSizes[match(TrimDataAgg$Comparison,EffSizes$comparison ),]$pvals
TrimDataAgg$Zvalue <- EffSizes[match(TrimDataAgg$Comparison,EffSizes$comparison ),]$zvals
TrimDataAgg$EffSize <- EffSizes[match(TrimDataAgg$Comparison,EffSizes$comparison ),]$statvals

rm(EffSizes, comparison, comparisons, pval,pvals,statvals, testres, teststat,testZ, zvals)

TrimDataAgg$pvalue <- as.numeric(as.vector(TrimDataAgg$pvalue))
TrimDataAgg$Zvalue <- as.numeric(as.vector(TrimDataAgg$Zvalue))
TrimDataAgg$EffSize <- as.numeric(as.vector(TrimDataAgg$EffSize))

TrimDataAgg$EffSize <- ifelse(TrimDataAgg$Response < 0.5,
                              TrimDataAgg$EffSize * -1,
                              TrimDataAgg$EffSize)

ggplot(data= TrimDataAgg, aes(x=Concurrent, y=Inducer, fill=EffSize)) +
  geom_tile(color = "white") +
  ggtitle("Biases - All Data- Effect Sizes") +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0, limit = c(-1,1),
                       name="Effect Size") +
  geom_text(aes(label = round(abs(EffSize), 2)), size = 4) +
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed() 


ggsave("Heatmap of All Data - Effect Sizes.png", plot = last_plot(), device = NULL, path = NULL,
  width = 10, height = 8, units = c("in", "cm", "mm"),
  dpi = 600)


```


So this is all of our effect sizes- some are obviously very small and some are very large - but we might want to only consider the ones that are significant- to do that we can subset the data or look at it in some other way 

```{r Correcting p for multiple comparisons}

TrimDataAgg$correctedP <- TrimDataAgg$pvalue * 93

TrimDataAgg$EffSize2 <- as.numeric(ifelse(TrimDataAgg$correctedP > 0.05,
                               "NA",
                               TrimDataAgg$EffSize))

TrimDataAgg$Response2 <- as.numeric(ifelse(TrimDataAgg$correctedP > 0.05,
                               "NA",
                               TrimDataAgg$Response))



ggplot(data= TrimDataAgg, aes(x=Concurrent, y=Inducer, fill=Response2)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white",
                       midpoint = 0.5, limit = c(0,1),
                       name="Direction and Strength of Association") +
  geom_text(aes(label = round(abs(EffSize), 2)), size = 4) +
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed() 


ggsave("Heatmap of All Data - Corrected Effect Sizes.png", plot = last_plot(), device = NULL, path = NULL,
  width = 10, height = 8, units = c("in", "cm", "mm"),
  dpi = 600)


```


So that's a pretty strict p value correction - strict bonferonni, which really doesn't seem appropriate given that the entire purpose of this study was to test a ton of associations

Lets look at some alternatives

```{r Corrections for Multiple Comparisons}

#Only responses that are significant to start with
TrimDataAgg$Response.Sig <- as.numeric(ifelse(TrimDataAgg$pvalue > 0.05,
                               "NA",
                               TrimDataAgg$Response))

#Bonferonni
TrimDataAgg$Response.Bonferonni <- TrimDataAgg$Response2

#Benjamini & Hockberg control for false discovery rate
TrimDataAgg$pvalue3 <- p.adjust(TrimDataAgg$pvalue, method= "BH")
TrimDataAgg$Response.BH <- as.numeric(ifelse(TrimDataAgg$pvalue3 > 0.05,
                               "NA",
                               TrimDataAgg$Response))
```

Now that we have these values we can plot them all - but that will require playing with the data structure a bit (and then melting it)


```{r Facet Wrap Plot of Significance w/ Various Types of Correction}

TrimDataAgg4 <- subset(TrimDataAgg, select = c(Inducer, Concurrent, Comparison, Response, Response.Sig, Response.BH, Response.Bonferonni))

colnames(TrimDataAgg4) <- c("Inducer", "Concurrent", "Comparison", "Uncorrected", "Significant", "Benjamini-Hochberg","Bonferonni")

library(reshape2)
TrimDataMelt <- melt(TrimDataAgg4,
                     variable.name = "Correction.Type",
                     value.name = "Response")


ggplot(data= TrimDataMelt, aes(x=Concurrent, y=Inducer, fill=Response)) +
  geom_tile(color = "white") +
  ggtitle("Biases - Corrected for Multiple Comparisons") +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0.5, limit = c(0,1),
                       name="Direction and Strength of Associaton") +
  geom_text(aes(label = round(Response, 2)), size = 3) +
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed() +
  facet_wrap(~ Correction.Type, ncol = 2)


ggsave("Biases - Corrected for Multiple Comparisons.png", plot = last_plot(), device = NULL, path = NULL,
  width = 12, height = 10, units = c("in", "cm", "mm"),
  dpi = 600)



```








