---
title: "Trial Setup - Color Experiment"
author: "Alan Nielsen"
date: "October 25, 2017"
output: html_document
---

Each participant is given each Color pair once as an inducer, and once as a concurrent for all of the other domains, for a total of 64 trials.

First, we will load in the packages we need

```{r Package Loading, message = FALSE}
library(tidyr) # for unite()
library(magrittr) # for pipe (%>%)
library(plyr)
```

Then, we will specify what all of the tokens are for each of the domains that we are interested in.
This creates a list of lists (roughly, a dictionary)

```{r Tokens}
Tokens <- list(Pitch = c("Hum", "Piano", "Pulse", "Tone"),
  Amp = c("Hum", "Piano", "Pulse", "Tone"),
  Noise = c("Hum", "Piano", "Pulse", "Tone"),
  Shape = c("BK1", "BK2", "BK3", "BK4"),
  Size = c("Circles", "Squares", "Triangles", "Diamonds"),
  Brightness = c("Circles", "Squares", "Triangles", "Diamonds"),
  Affect = c("EB", "HS", "PD", "SC"),
  Speed = c("SP1", "SP2", "SP3", "SP4"))

Domains <- names(Tokens)
```



```{r WriteStimuli Function}

createstimuli <- function() {
  
  ColorTokens <- c("RG", "RY", "YB", "RB") 
  Inducers <- expand.grid(Inducer = ColorTokens, Concurrent = Domains)        #1 - Create relevant combinations
  Concurrents <- expand.grid(Inducer = Domains, Concurrent = ColorTokens)

  Inducers <- Inducers[order(Inducers$Concurrent),]
  Concurrents <- Concurrents[order(Concurrents$Inducer),]
  NonFocalTokens <-c(sapply(Domains, function(d) sample(Tokens[[d]], 1)))   #2 Assign tokens for non-focal domains
  Inducers$ConcurrentToken <- rep(NonFocalTokens, each=4)
  Concurrents$InducerToken <- rep(NonFocalTokens, each=4)
  Inducers$InducerToken <- Inducers$Inducer
  Concurrents$ConcurrentToken <- Concurrents$Concurrent
  Inducers$Inducer <- "Color"
  Concurrents$Concurrent <- "Color"
  
  
  TrialList <- rbind(Inducers, Concurrents)                       #Randomize trial type
  TrialList$TrialType <- rep(sample(1:4),16)
  TrialList$Focal1 <- "Color"
  
  TrialList$InducerL <- mapvalues(TrialList$TrialType,
                                  from = c(1, 2, 3, 4),
                                  to = c("H", "H", "L", "L"))
  TrialList$InducerR <- mapvalues(TrialList$TrialType,
                                  from = c(1, 2, 3, 4),
                                  to = c("L", "L", "H", "H"))     #4 Assign locations for all stims
  
    
   TrialList$ConcurrentL <- mapvalues(TrialList$TrialType,
                                  from = c(1, 2, 3, 4),
                                  to = c("H", "L", "H", "L"))
  TrialList$ConcurrentR <- mapvalues(TrialList$TrialType,
                                  from = c(1, 2, 3, 4),
                                  to = c("L", "H", "L", "H"))   
  
  TrialList$InducerL <- with(TrialList, paste(Inducer, InducerToken, InducerL, sep = '-'))
  TrialList$InducerR <- with(TrialList, paste(Inducer, InducerToken, InducerR, sep = '-'))
  TrialList$ConcurrentL <- with(TrialList, paste(Concurrent, ConcurrentToken, ConcurrentL, sep = '-'))
  TrialList$ConcurrentR <- with(TrialList, paste(Concurrent, ConcurrentToken, ConcurrentR, sep = '-'))

  TrialList <- TrialList[sample(nrow(TrialList)), ]                   #5 Shuffle the order of trials
  TrialList$TrialNum <- seq(nrow(TrialList))
  
  TrialList <- subset(TrialList, select=c("TrialNum", "Focal1", "Inducer", "Concurrent", "TrialType",
                      "InducerL", "InducerR", "ConcurrentL", "ConcurrentR"))

  ########################
  # Finally just a bit of cleanup

  return(TrialList)
}

```
So that's our CreateStimuli function, which outputs us a stimlist as a data frame.

All we need to do is save this data frame as a CSV (which can then be read by our jsPsych code), and of course to do that multiple times- we need to generate a large number of stimlists - one for each participant in this version of the experiment

To do that, we'll write another function, and inside of that function we will call the CreateStimuli function a number of times

```{r WriteStimuli}
writestimuli <- function(n, conditionname= "Color") {
  # do n times, storing the current iteration number in 'i'
  for (i in 1:n) {
    # create stimuli data frame. 'dimensions' is already in the right format so
    # just pass it on directly
    stimuli <- createstimuli()
    # add participant 'Id' column (concatenation of the conditionname and 'i')
    stimuli <- cbind(Id=paste(conditionname, i, sep="-"), stimuli)
    # write resulting data frame to a file
    write.table(stimuli,
      paste("F:/GitHub Repos/Crossmodality-Toolkit/Stimuli/Stimlists/Color/", "Stimuli-", conditionname, "-", i, ".csv", sep=""),
      sep = "\t", row.names=FALSE)
  }
}

```


Then finally, we just need to call our writestimuli a number of times, once for each stimlist that we want- in this case we are going to be running 60 participants, but lets generate 100 stimlists, just to be on the safe side.

```{r Outputting Stimlist Files}
writestimuli(60)

```











